Political Support in the United States

### 2024-03-16 paper/paper.qmd
Update paper.qmd

# Introduction

The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems. This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance. With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.

@@

The data utilized for analysis, including both survey and census data, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. I will also talk about the predicted results derived from the model in Section 4. Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).

>>>>

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems. This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance. With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.

@@

Throughout the paper, the data utilized for analysis, including both survey and census data, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. I will also talk about the predicted results derived from the model in Section 4. Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).
